Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2022-01-03 Scripts/Initial_Analysis.Rmd
Misc.

    # Min, max and median change per eez_name and neighbor
    eez_summary <- spp %>% 
      group_by(eez_name,eez_neighbour,time_step) %>% 
      summarise(
        n_spp = length(unique(taxon_key)),
        n_stock = n(),
        min_eez = min(mean_spp, na.rm=T),
        max_eez = max(mean_spp, na.rm=T),
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = median(mean_spp,na.rm=T)
      ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez,n_spp,n_stock) %>% 
      left_join(n_ssr)

@@

    eez_summary <- spp %>% 
      group_by(eez_name,time_step) %>% 
      summarise(
        n_spp = length(unique(taxon_key)),
        n_stock = n(),
        min_eez = min(mean_spp, na.rm=T),
        max_eez = max(mean_spp, na.rm=T),
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = mean(mean_spp,na.rm=T)
      ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez,n_spp,n_stock)

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_spp:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2) # original
    )
    )
    )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
         avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per)) %>% 
  filter(time_step == time_toplot)

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            # left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  # left_join(Eez_centroid_eck,
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
         avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per))

>>>>

    # Min, max and median change per eez_name and neighbor
    eez_summary <- spp %>% 
      group_by(eez_name,eez_neighbour,time_step) %>% 
      summarise(
        # n_spp = length(unique(taxon_key)),
        n_stock = n(), # Number of shifting stocks
        min_eez = min(mean_spp, na.rm=T), #minimum proportion across all shifting stocks
        max_eez = max(mean_spp, na.rm=T), # maximum proportion across all shifting stocks
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = median(mean_spp,na.rm=T) # mean proportion across all shifting stocks
      ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez,n_stock) %>% 
      left_join(n_ssr)

@@

    eez_summary <- spp %>% 
      group_by(eez_name,time_step) %>% 
      summarise(
        # n_spp = length(unique(taxon_key)),
        n_stock = n(),
        min_eez = min(mean_spp, na.rm=T),
        max_eez = max(mean_spp, na.rm=T),
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = mean(mean_spp,na.rm=T)
      ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez,n_stock)

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_stock:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2) # original
    )
    )
    )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_stock") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
         avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per)) %>% 
  filter(time_step == time_toplot)

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            # left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  # left_join(Eez_centroid_eck,
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_stock")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_stock") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
         avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per))
